Predicting the conformational preferences of proteins using a physics-based free energy method

### 2013-04-24 Paper/paper.tex
changed CASP summery

Second, we looked at 6 target proteins from the CASP9 experiment.  For each target, we examined up to 5 submitted models.  We 
computed the difference free energy between the true native and the best model.  Table~\ref{table:casp_control} shows that, in 5 
out of 6 cases, the confinement method assigns a lower free energy to the experimentally determined structure than to any of the 
decoys.  Other well-known discriminators  can also successfully make this recognition \cite{Sheffler2009}; 
 it is just an independent useful validation that the confinement calculations make sense.

>>>>

Second, we looked at 6 target proteins from the CASP9 experiment.  For each target, we examined up to 5 submitted models.  We 
computed the difference free energy between the true native and the best model. Figure~\ref{fig:summary_casp} and 
Table~\ref{table:casp_control} shows that, in 5 
out of 6 cases, the confinement method assigns a lower free energy to the experimentally determined structure than to any of the 
decoys.  Other well-known discriminators  can also successfully make this recognition \cite{Sheffler2009}; 
 it is just an independent useful validation that the confinement calculations make sense.

\begin{figure}
\begin{center}
\includegraphics[width=3.5 in,height=3.2 in]{casp.pdf}
\end{center}
\caption{In 5 out of 6 CASP Target, the confinement method assigns a lower free energy to the experimentally determined native structure.} 
\label{fig:summary_casp}
\end{figure}
